Concurrent Programming with Harmony

### 2020-08-13 book/paper.tex
Latest

\begin{figure}
\begin{code}
\harmonysource{xy}
\end{code}
\caption{$x + y = 100$.}
\label{fig:xy}
\end{figure}

@@

The \texttt{alloc} module
\index{alloc module}%
maintains a pool of ``memory locations'' and
supports thread-safe (but not interrupt-safe) dynamic allocation of
memory locations.  There are just two methods:

@@

The usage is similar to \texttt{malloc} and \texttt{free} in C.
\texttt{malloc}() returns \texttt{None} when running out of memory.

>>>>

\begin{figure}
\begin{code}
\harmonysource{xy}
\end{code}
\caption{Imcomplete code with desired invariant $x + y = 100$.}
\label{fig:xy}
\end{figure}

@@

The \texttt{alloc} module
\index{alloc module}%
supports thread-safe (but not interrupt-safe) dynamic allocation of
memory locations.  There are just two methods:

@@

The usage is similar to \texttt{malloc} and \texttt{free} in C.
\texttt{malloc}() is specified to \texttt{None} when running out of
memory, although this is an impossible outcome in the current
implementation of the module.
